---
title       : Shiny App Presentation
subtitle    : October 26, 2016
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github      :
    user: fvf1361
    repo: DataProducts
---

## Introduction
The shiny app uses the father.son dataset.  
The objective of this app is to demonstrate the importance of proper sampling in data analysis.  

---

## Exploratory data analysis
Here is a summary of the dataset

```{r exploratory, echo=TRUE, message=FALSE, warning=FALSE}
library(UsingR)
data("father.son")
summary(father.son)
```

---

## The App
There are three parts in the app that the user can control. In order to run the app successfully, the following steps should be followed:

> 1. Determine the range of data that goes into training using the first slider bar.
> 2. Decide if the regression line is to be displayed or not by toggling the checkbox on/off.
> 3. Assign the Value used for testing

---

## Results
The black line is the regression line, and the vertical line is the value for which the son's height is estimated.  
The red dot shows the estimated height for the given father's height.  
```{r FinalPlot, echo=FALSE, warning=FALSE, message=FALSE}
fs <- as.data.frame(father.son)
x <- fs$fheight
y <- fs$sheight
plot(x,y, xlab = "father's height (inches)", ylab = "son's height (inches)", xlim = c(58, 77), ylim = c(58,80), pch=19, col="blue")
abline(v=71, lwd=2, col="red")
fit1 <- lm(y~x)
a <- fit1$coefficients[2]
b <- fit1$coefficients[1]
abline(reg=fit1, lwd = 2, col="black")
points(71, a*71+b, pch=16, cex=2, col="red")
```